---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r, echo=FALSE}
# Define variable containing url
url_map <- "https://pbs.twimg.com/media/Ek4TtIpXYAAhwSB?format=png&name=4096x4096"
```

# map1968

<!-- badges: start -->
<!-- badges: end -->

This is a quick project to plot lovable hand-drawn esque election maps to the style of the New York Times' 1968 election map:

<center><img src="`r url_map`"></center>

Inspired by [this tweet](https://twitter.com/alv9n/status/1319013784346906629) showing interest in the simple, yet elegant polygons created for this map, I decideed to trace the map as an svg and georeference to a geojson file, so someone could easily plot this map with fill based on vote count or other data.

The map is available as an svg in this repo with path ids defined as the state postal code:


![svg of 1968 NYT election map](elections_fill.svg)   

It is also available as a plottable geojson file.

Simply read in the file, tidy it, and plot it with geom_polygon.

```{r plot, warning = FALSE, message = FALSE}

library(geojsonio)
library(broom)
library(sp)
library(dplyr) #for pipes

spdf <- geojsonio::geojson_read("./elections_features.geojson",  what = "sp")


spdf_fortified <- broom::tidy(spdf) %>% dplyr::filter(!id==1)

library(ggplot2)

ggplot() +
  geom_polygon(data = spdf_fortified, aes( x = long, y = lat, group = group), fill = NA, colour = "#00abff") +
  theme_void() +
  coord_map()

```

The plan is to set each polygon to have the state postal code to be easily bound to election data before the 2020 presidential election.

Feel free to clone or fork the repo if you would like to use the files or [DM me](https://twitter.com/_willdebras) if you have questions.